Astr 513: Final Project

### 2016-05-09 Final_Project/ms.tex
Added Rest LCDM with priors plots and data to tex file
Updated best fit for Rest wCDM with priors
Updated the best fit, and also corrected the name of the plot file for
Rest LCDM with priors in the tex file. It should all run now.

    Rest et al.                & 0      & 0 \\

@@

@@

    Rest et al.                & $0.4 \pm 0.3$                      & $0.68 \pm 0.06$     & $-1.1 \pm 0.6$     \\

@@

  \includegraphics[width=0.5\linewidth]{figures/rest_wcdm_withpriors_corner.eps}

>>>>

    Rest et al.                & $0.322 \pm 0.003$      & $0.659 \pm 0.002$ \\

@@

  \includegraphics[width=0.5\linewidth]{figures/rest_lcdm_noprior_corner.eps}
  \includegraphics[width=0.5\linewidth]{figures/rest_lcdm_withprior_corner.eps}
    analysis of the \citet{rest2014} data for a $\Lambda$CDM model. Contours denote the
    \Planck priors. {\it Right}: with \Planck priors.
  \TM{The figure on the right didn't appear in the repo. Please upload.}}
  \label{fig:rest_lcdm_corner}

@@

    Rest et al.                & $0.295 \pm 0.003$                      & $0.658 \pm 0.002$     & $-0.827 \pm 0.007$     \\

@@

  \includegraphics[width=0.5\linewidth]{figures/rest_wcdm_withprior_corner.eps}
